Bird beak's elaboration and innovation

### 2022-07-15 Analysis/03-Elaboration_innovation_analysis.Rmd
added passeriformes results

>>>>

```{r, echo = FALSE, eval = FALSE}
load("../Data/Processed/shapespace_passeriformes_suborder_family_results_list.rda")
results <- shapespace_passeriformes_suborder_family_results_list
rm(shapespace_passeriformes_suborder_family_results_list)
## Getting the plotting data
ploting_data_passeriformes <- list(
                     "median_elaborations" = apply(get.disparity(get.subsets(results$suborder_results_phylo$position, subsets = "phylogeny"), concatenate = FALSE)[[1]], 1, median),
                     "median_innovations"  = apply(get.disparity(get.subsets(results$suborder_results_phylo$distance, subsets = "phylogeny"), concatenate = FALSE)[[1]], 1, median),
                     "distances_to_centre" = get.disparity(dispRity(get.subsets(suborder_shapespace, subsets = "phylogeny"), metric = dispRity::centroids, centroid = 0))[[1]],
                     "consensus_tree"      = tree)

## Getting the plotting data super_order_level
ploting_data_passeriformes_suborder <- list(
                     "median_elaborations" = get.macro.projection(results$suborder_results_within, what = "position"),
                     "median_innovations"  = get.macro.projection(results$suborder_results_within, what = "distance"),
                     "distances_to_centre" = get.macro.projection(suborder_shapespace, what = "centroids"),
                     "consensus_tree"      = tree)

## Getting the plotting data super_order_level
ploting_data_passeriformes_family <- list(
                     "median_elaborations" = get.macro.projection(results$family_results_within, what = "position"),
                     "median_innovations"  = get.macro.projection(results$family_results_within, what = "distance"),
                     "distances_to_centre" = get.macro.projection(family_shapespace, what = "centroids"),
                     "consensus_tree"      = tree)

## Save all that as a list
save(ploting_data_passeriformes, file = "../Data/Processed/ploting_data_passeriformes.rda")
## The projections within the suborders
save(ploting_data_passeriformes_suborder, file = "../Data/Processed/ploting_data_passeriformes_suborder.rda")
## The projections within the families
save(ploting_data_passeriformes_family, file = "../Data/Processed/ploting_data_passeriformes_family.rda")

## Group info
suborders <- lapply(results$suborder_results_phylo$position$subsets, function(x, data) list(species = rownames(data)[c(x$elements)]), data = results$suborder_results_phylo$position$matrix[[1]])
families <- lapply(results$family_results_phylo$position$subsets, function(x, data) list(species = rownames(data)[c(x$elements)]), data = results$family_results_phylo$position$matrix[[1]])
## Adding the colours
load("../Data/Processed/tip_colours_suborders.rda")
load("../Data/Processed/tip_colours_families.rda")
add.col <- function(one_order, one_col) {
    one_order$col <- one_col
    return(one_order)
}
suborders <- mapply(add.col, one_order = suborders[1:8][match(names(suborders[1:8]), names(tip_colours_suborders))], one_col = as.list(tip_colours_suborders), SIMPLIFY = FALSE)
families <- mapply(add.col, one_order = families[1:27][match(names(families[1:27]), names(tip_colours_families))], one_col = as.list(tip_colours_families), SIMPLIFY = FALSE)

## Big list:
clade_info_passeriformes <- list(suborders = suborders,
                                 families = families)
## Save all that data
save(clade_info_passeriformes, file = "../Data/Processed/clade_info_passeriformes.rda")
```
